Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-10 cordillera-cycle.tex
Add 6-km resolution time-series.

% fig:timeseries
\begin{figure}
  \includegraphics{timeseries}
  \caption{Temperature offset time-series from ice core and sediment core
           records (Table~\ref{tab:records}) used as palaeo-climate forcing for
           the ice sheet model \textbf{(top)}, and modelled ice volume
           through the last 120\,\unit{kyr}, expressed in meters of sea-level
           equivalent \textbf{(bottom)}. Gray spans indicate Marine Isotope
           Stages (MIS) according to a global compilation of benthic
           \chem{\delta^{18}O} records \citep{lisiecki-raymo-2005}. Hatched
           rectangles indicate modelled ice volume extrema corresponding to
           MIS~4 (61.9--55.4\,\unit{kyr}), MIS~3 (52.2--45.6\,\unit{kyr}), and
           MIS~2 (last glacial maximum, 29.5--16.9\,\unit{kyr}).}
  \label{fig:timeseries}
\end{figure}

>>>>

% fig:timeseries
\begin{figure}
  \includegraphics{timeseries}
  \caption{Temperature offset time-series from ice core and sediment core
           records (Table~\ref{tab:records}) used as palaeo-climate forcing for
           the ice sheet model \textbf{(top)}, and modelled ice volume
           through the last 120\,\unit{kyr}, expressed in meters of sea-level
           equivalent \textbf{(bottom)}. Gray spans indicate Marine Isotope
           Stages (MIS) according to a global compilation of benthic
           \chem{\delta^{18}O} records \citep{lisiecki-raymo-2005}. Hatched
           rectangles highlight modelled ice volume extrema corresponding to
           MIS~4 (61.9--55.4\,\unit{kyr}), MIS~3 (52.2--45.6\,\unit{kyr}), and
           MIS~2 (last glacial maximum, 29.5--16.9\,\unit{kyr}). Dotted lines
           correspond to the GRIP and EPICA 6\,\unit{km}-resolution runs.}
  \label{fig:timeseries}
\end{figure}
